\Title

### 2016-02-12 manuscript/manuscript.tex
Caption for crust1 synthetic data figure
Add seismic points to crust1 data figure
Had to make the figure whole page and include the new plot  in the
caption.

>>>>

\begin{figure*}
    \centering
    \includegraphics{figures/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Synthetic seismic data simulating point estimates of Moho depth.
        The point estimates were obtained by interpolating
        the Moho depth in (a).
    }
    \label{fig:crust1-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[]{figures/synthetic-crust1-results}
    \caption{
    CRUST1 results.
    }
    \label{fig:crust1-results}
\end{figure*}
